Title here

### 2016-08-11 portfolio/text/ms.Rmd
Update figures
Update text
Tweak fig sizes

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{../figs/stan-across-strategy-variability.pdf}
\caption{Caption here}
\label{fig:across}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-gg-spoke2.pdf}
\caption{Caption here}
\label{fig:spokes}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../figs/offset-break-anti-spaghetti.pdf}
\caption{Caption here}
\label{fig:within}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/fig1-jk.pdf}
\caption{Caption here}
\label{fig:ts}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../figs/stan-gg-spoke2.pdf}
\caption{Caption here}
\label{fig:spokes}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability.pdf}
\caption{Caption here}
\label{fig:across}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.1\textwidth]{../figs/stan-offset-break-anti-spaghetti.pdf}
\caption{Caption here}
\label{fig:within}
\end{center}
\end{figure}
